---
output:
  pdf_document: default
  html_document: default
---
## DV2 – HW2
*CEU BA*

*Ersan Kucukoglu - 1904225*

`r format(Sys.time(), '%d %B, %Y')`

### 0. Load the nycflights13 package and check what kind of datasets exist in the package, then create a copy of flights dataset into a data.table object, called flight_data.

```{r,message=FALSE, warning=FALSE}
#load the nycflights13 package
library(nycflights13)
#check datasets
data(package='nycflights13')
#flights dataset
library(data.table)
flight_data <- as.data.table(nycflights13::flights)
```
### 1. Which destination had the lowest avg arrival delay from LGA with minimum 100 flight to that destination?

```{r,echo=FALSE,warning=FALSE,message=FALSE}
flight_data[origin=="LGA", 
            .(avg_arr_delay=mean(arr_delay,na.rm = TRUE), no_flights= .N), 
            by=.(destination=dest)][no_flights >= 100][order(avg_arr_delay)][1]
```

### 2. Which destination's flights were the most on time (avg arrival delay closest to zero) from LGA with minimum 100 flight to that destination?

```{r,echo=FALSE,warning=FALSE,message=FALSE}
var1 <- flight_data[origin=="LGA", 
                    .(avg_arr_delay=mean(arr_delay,na.rm = TRUE), no_flights= .N), 
                    by=.(destination=dest)][no_flights >= 100]

var1[avg_arr_delay %between% c(-1,1),][order(avg_arr_delay)][1]
```

### 3. Who is the manufacturer of the plane, which flights the most to CHS destination?

```{r,echo=FALSE,warning=FALSE,message=FALSE}
planes <- as.data.table(nycflights13::planes)
df <- merge.data.table(flight_data,planes,by='tailnum')

df[dest=="CHS",.(no_flight= .N),by=.(tailnum,manufacturer)][order(no_flight)][.N]
```

### 4. Which airline (carrier) flow the most by distance?

```{r,echo=FALSE,warning=FALSE,message=FALSE}
flight_data[,.(total_distance=sum(distance)),by="carrier"][order(total_distance)][.N]
```

### 5. Plot the monthly number of flights with 20+ mins arrival delay!

```{r,echo=FALSE,warning=FALSE, message=FALSE}
library(ggplot2)
library(lubridate)
q5 <- flight_data[arr_delay > 20, list(date = make_date(year, month))]
p1 <- ggplot(q5, aes(x = date)) + geom_bar()+
      labs(title = "Monthly number of flights with 20+ mins arrival delay",
       subtitle = "20+ arrival delay",
       x="Months", 
       y= "Number of Flights")
p1

```

### 6. Plot the departure delay of flights going to IAH and the related day's wind speed on a scaterplot! Is there any association between the two variables? Try adding a linear model.

```{r,echo=FALSE,warning=FALSE, message=FALSE}
weather <- as.data.table(nycflights13::weather)

df2 <- merge(
  flight_data[dest=="IAH",.(dest,dep_delay), by = .(year, month, day, origin)],
  weather[, .(avg_wind_speed=mean(wind_speed,na.rm = T)), by = .(year, month, day, origin)],
  by = c("year", "month", "day",  "origin"))
 
p2 <- ggplot(df2, aes(x=dep_delay,y=avg_wind_speed))+geom_point()+
  geom_smooth(method = 'lm',formula = y~x)+
  labs(title = "Association between Departure delay and Wind Speed",
       subtitle = "Destination : IAH",
       x="Departure Delay", 
       y= "Mean of wind speed")
p2
```

### 7. Plot the airports as per their geolocation on a world map, by mapping the number flights going to that destionation to the size of the symbol!

```{r,echo=FALSE, warning=FALSE, message=FALSE}
# Libraries
library(ggplot2)
library(dplyr)
# some standard map packages.
#install.packages(c("maps", "mapdata"))
library(maps)
world <- map_data("world")

airports <- as.data.table(nycflights13::airports)
airports$dest <- airports$faa
flights2 <- flight_data[,.(total_flight=.N),by=dest]

df3 <- left_join(flights2,airports,by="dest") 

g <- ggplot(data=world)
g2 <- g + geom_polygon(mapping=aes(x=long,y=lat,group=group),color="white",fill="grey")

g3 <- g2 + geom_point(data=df3, mapping = aes(x = lon, y = lat,size=total_flight), 
                      position = "jitter")
g3

#alternative way
ggplot()+
  geom_polygon(
    data=world,
    aes(x=long,y=lat,group=group),color="white",fill="grey")+
  geom_point(merge( airports,
                    data.table(flight_data)[,.(total_flight=.N),by=.(faa=dest)],
                    by='faa'),
             aes(x=lon,y=lat,size=total_flight),
             color = 'orange')+
  theme_bw()+
  xlab('')+ylab('')+
  theme(legend.position = 'top')+
  coord_fixed(1.3)
  
```


